### 2019-08-29 Writeup/Thesis/chapters/evaluation.tex
Changes; - All fixes implemented from supervisor feedback

\section{Research Question \ref{goal:complexity}}
Research Question \ref{goal:complexity}: \textit{``What are the time and computation complexity required to generate a ’similar’ keys for a targeted key pair?''} has been discussed by the project, the actual generation of keys as shown in Section \ref{sec:key_gen} where actual keys were generated. Furthermore, the distribution of key permutations on a set of real-world keys were discussed in Section \ref{sec:averagePerms} and \ref{sec:vulnKeys}. To achieve this, the tool GreenOnion was developed where inspiration was gathered from a currently available tool known as Scallion. Experimentation results were gathered and displayed in Section \ref{sec:SvG} that showed the significant increase in the number of near-collision keys GreenOnion can test for with GreenOnion being able to handle in excess of 1.5 million keys. This capability is in comparison to the maximum of 40 keys Scallion can compare. We believe this is due to the implementation of the bloom filter. Its unique characteristics of $O(k)$ complexity regardless of number of elements in the structure results in a huge number of concurrent checks to occur.

>>>>

\section{Research Question \ref{goal:complexity}}
Research Question \ref{goal:complexity}: \textit{``What are the time and computation complexity required to generate a ’similar’ keys for a targeted key pair?''} has been discussed by the project, the actual generation of keys as shown in Section \ref{sec:key_gen} where actual keys were generated. Furthermore, the distribution of key permutations on a set of real-world keys were discussed in Section \ref{sec:averagePerms} and \ref{sec:vulnKeys}. To achieve this, the tool GreenOnion was developed where inspiration was gathered from a currently available tool known as Scallion. Experimentation results were gathered and displayed in Section \ref{sec:SvG} that showed the significant increase in the number of near-collision keys GreenOnion can test for with GreenOnion being able to handle in excess of 1.5 million keys. This capability is in comparison to the maximum of 2513 keys Scallion can compare. We believe this is due to the implementation of the bloom filter. Its unique characteristics of $O(k)$ complexity regardless of number of elements in the structure allows a huge number of concurrent checks to occur.

### 2019-08-29 Writeup/Thesis/chapters/experiments.tex
Changes; - All fixes implemented from supervisor feedback

\todo{Talk about the exception}

\begin{wraptable}[11]{r}{6cm}
    \centering
    \begin{tabular}{|ll|}
        \hline
        \textbf{Scallion} & \\
        \hline
        OS & Windows 10 (May 2019) \\
        Version & Scallion-2.0\footnote{\url{https://github.com/lachesis/scallion/raw/binaries/scallion-v2.0.zip}} \\
        \hline
        \textbf{GreenOnion} & \\
        \hline
        OS & Linux Mint (Version: TODO) \\ 
        \hline
        \textbf{Hardware} & \\
        \hline
        GPU & GTX 750 Ti  \\
        CPU & AMD FX-6300 \\
        \hline
    \end{tabular}
    \caption{Testing environment}
\end{wraptable}

@@

Figure \ref{tab:scallion_speed} shows the speed decline as the number of potential keys checked in one go increases for Scallion. Any number of keys over 40 resulted in a crash for Scallion. This crash is solely due to an  implementation issue.

\todo{Fix implementation issue}

GreenOnion's speed is almost perfectly consistent. It is slower up until  around 5 keys. This consistency is due to the overhead of the bloom filter; however, as the number of keys increase, the bloom filter's benefits become apparent. In this test, the bloom filter size was kept consistent at exactly 5,000 elements.

GreenOnion has been tested to handle more than 1.5 million keys with a slight reduction in performance. This improvement over Scallion is, therefore, substantial.

GreenOnion's code has been made publicly available on GitHub \footnotemark{TODO}.

@@

\todo{Include comparison to Hash-Friendly Schemes paper as they used Transposition to create 'Hard Matches' i.e. blub --> bulb}

@@

\begin{table}[!h]
    \makebox[\textwidth][c]{
        \centering
        \begin{tabular}{|lllll|}
            \hline
            \textbf{Metric} & & \textbf{Mean matches} & \textbf{$\sigma$} & \textbf{Compute Time} \\
            \hline
            NYSIIS &&&& \\
            \hline
            & 0 static & 1963.07 & 24769.48 & ~~27.19 days \\
            & 1 static & 448.37 & 4316.57 & 119.14 days \\
            & 2 static & 98.07 & 550.44 & ~~~~1.49 years \\
            \hline

            Metaphone &&&& \\
            \hline
            & 0 static & 27138.78 & 529229.35 & ~~~~1.97 days \\
            & 1 static & 2822.74 & 23932.39 & ~~18.91 days \\
            & 2 static & 339.84 & 1730.97 & 157.45 days \\
            \hline

            Levenshtein &&&& \\
            \hline
            & 0 static & 293.92 & 2158.24 & 182.17 days \\
            & 1 static & 102.75 & 719.28 & ~~~~1.43 years \\
            & 2 static & 35.53 & 120.71 & ~~~~4.18 years \\
            \hline

        \end{tabular}
    }
    \caption{Each metric's average number of near-collision keys}
    \label{tab:average_perm}
\end{table}

@@

\section{Distribution of vulnerable keys}
\label{sec:vulnKeys}
As discussed in the design of the second experiment (See Section \ref{sec:exp2}), the attacks sampled from a list of `vulnerable keys'. These vulnerable keys were created using real keys extracted from PGP key servers. These keys were then randomly sampled and used to create the combined key,as discussed in Section \ref{sec:pep}. 100,000 random key pairs were created and used as the sample. Any vulnerable keys in this set were recorded and used in the experiment.

\todo{Reference David's work}

@@

        \begin{tabular}{|lll|}
            \hline
            \textbf{Attack Type} & \textbf{Metric} & \textbf{Vulnerable \%} \\
            \hline 
            2 static (152) && \\ 
            & Levenshtein & ~~4.295\% \\
            & Metaphone & 24.095\% \\
            & NYSIIS & 10.441\% \\
            \hline
            1 static (1525) && \\ 
            & Levenshtein & ~~0.827\% \\
            & Metaphone & 15.569\% \\
            & NYSIIS & ~~4.341\% \\
            \hline
            0 static (15250) && \\ 
            & Levenshtein & ~~0.157\% \\
            & Metaphone & 10.202\% \\
            & NYSIIS & ~~1.824\% \\
            \hline
        \end{tabular}
    }
    \caption{Number of vulnerable keys per metric}
    \label{tab:vulnkeys}
\end{table}

@@

\section{Generation of keys}
\label{sec:key_gen}
In order to demonstrate that the generation of the near-collision keys is not only theoretical, the actual generation of keys was performed using GreenOnion. A random metric was selected from the three carried forward from the first experiment. Alongside this, a random uncontrolled key was generated as the simulated attack target (See Appendix \ref{appendix:uncontrolled_key} for the armor public key). Then for each attack level (0 static, 1 static, 2 static), a key was computed. NYSIIS was chosen as the selected metric. To expedite the process, an initial search was performed for controlled keys that had the highest number of near-collisions; this was due to the demonstrative purpose of this experiment. Producing near-matching keys from key pairs with a very small number of potential matches adds very little to this demonstration.

>>>>

@@

Figure \ref{tab:scallion_speed} shows the speed decline as the number of concurrently checked potential keys increases. Alongside the results for base version of Scallion is the speed for \textit{Scallion Improved}. This is the same Scallion code but with a fix that reduces the severity of the speed decline.

\begin{table}[h!]
    \centering
    \begin{tabular}{|ll|}
        \hline
        \textbf{Scallion} & \\
        \hline
        OS & Windows 10 (May 2019) \\
        Version & Scallion 2.1 (Commit: \verb|42b4cb5|\footnote{\url{https://github.com/lachesis/scallion/tree/42b4cb555dbf8554b212a2bc3e0ba3d652434ecf}}) \\
        \hline
        \textbf{GreenOnion} & \\
        \hline
        OS  & Linux Mint 19.1 \\
            & Kernel: 4.15.0 \\ 
        \hline
        \textbf{Hardware} & \\
        \hline
        GPU & Nvidia GTX 750 Ti  \\
        CPU & AMD FX-6300 \\
        \hline
    \end{tabular}
    \caption{Testing environment}
\end{table}

Figure \ref{fig:scallionCode} contains a snippet of code with the error. The calls to \verb|parms.ToolConfig.PredictRuntime()| become increasingly expensive as the number of concurrently checked keys increases. Removing this line from the \verb|Console.Write| statement results in a sizeable improvement in speeds as can be seen in Figure \ref{tab:scallion_speed}. This was necessary to include as we believe the improved versions show a better comparison between the design of the two tools.

\begin{figure}[h!]
    \input{code/scallion_bug.tex}
    \caption{Scallion's main print statement}
    \label{fig:scallionCode}
\end{figure}

GreenOnion's speed is almost perfectly consistent. It is slower up until  around 800 keys. This initial lower speed is due to the overhead of the bloom filter; however, as the number of keys increase, the bloom filter's benefits become apparent. In this test, the bloom filter size was kept consistent at exactly 10,000 elements.

Scallion was unable to handle anything over 2513 concurrent keys. This was due to the search strings being passed via a command line argument as a regex string. This number of keys hit the character limit of a Powershell command. GreenOnion, however, has been tested to handle more than 1.5 million keys with a slight reduction in performance. This improvement over Scallion is, therefore, substantial.

GreenOnion's code has been made publicly available and can be viewed on GitHub\footnote{\url{https://github.com/AidanFray/GreenOnion}}.

@@

@@

\begin{table}[!h]
    \makebox[\textwidth][c]{
        \centering
        \begin{tabular}{|llll|}
            \hline
            \textbf{Metric} & & \textbf{Mean matches} & \textbf{Compute Time} \\
            \hline
            NYSIIS &&& \\
            \hline
            & 0 static & 1963.07 &  ~~27.19 days \\
            & 1 static & 448.37 &  119.14 days \\
            & 2 static & 98.07 &  ~~~~1.49 years \\
            \hline\hline

            Metaphone &&& \\
            \hline
            & 0 static & 27138.78 &  ~~~~1.97 days \\
            & 1 static & 2822.74 &  ~~18.91 days \\
            & 2 static & 339.84 &  157.45 days \\
            \hline\hline

            Levenshtein &&& \\
            \hline
            & 0 static & 293.92 &  182.17 days \\
            & 1 static & 102.75 &  ~~~~1.43 years \\
            & 2 static & 35.53 &   ~~~~4.18 years \\
            \hline\hline

        \end{tabular}
    }
    \caption{Each metric's average number of near-collision keys and average compute times}
    \label{tab:average_perm}
\end{table}

@@

\section{Distribution of vulnerable keys}
\label{sec:vulnKeys}
As discussed in the design of the second experiment (See Section \ref{sec:exp2}), the attacks sampled from a list of `vulnerable keys'. These vulnerable keys were created using real keys extracted from PGP key servers. These keys were then randomly sampled and used to create the combined key,as discussed in Section \ref{sec:pep}. 100,000 random key pairs were created and used as the sample\cite{davidnorman_2019}. Any vulnerable keys in this set were recorded and used in the experiment.

@@

        \begin{tabular}{|lll|}
            \hline
            \textbf{Attack Type} & \textbf{Metric} & \textbf{Vulnerable \%} \\
            \hline 
            2 static (152) && \\ 
            & Levenshtein & ~~4.295\% \\
            & Metaphone & 24.095\% \\
            & NYSIIS & 10.441\% \\
            \hline\hline
            1 static (1525) && \\ 
            & Levenshtein & ~~0.827\% \\
            & Metaphone & 15.569\% \\
            & NYSIIS & ~~4.341\% \\
            \hline\hline
            0 static (15250) && \\ 
            & Levenshtein & ~~0.157\% \\
            & Metaphone & 10.202\% \\
            & NYSIIS & ~~1.824\% \\
            \hline\hline
        \end{tabular}
    }
    \caption{Number of vulnerable keys per metric}
    \label{tab:vulnkeys}
\end{table}

@@

\section{Generation of keys}
\label{sec:key_gen}
In order to demonstrate that the generation of the near-collision keys is not only theoretical, the actual generation of keys was performed using GreenOnion. A random metric was selected from the three carried forward from the first experiment. Alongside this, a random uncontrolled key was generated as the simulated attack target (See Appendix \ref{appendix:uncontrolled_key} for the armor public key). Then for each attack level (0 static, 1 static, 2 static), a key was computed. NYSIIS was chosen as the selected metric. To expedite the process, an initial search was performed for controlled keys that had the highest number of near-collisions; this was due to the demonstrative purpose of this experiment. Producing near-matching keys from key pairs with a very small number of potential matches adds very little to this demonstration. This, however, will result in best-case scenario key computation times.

### 2019-08-29 Writeup/Thesis/chapters/lit_review.tex
Changes; - Implemted changes from Sia - Added abstract and acknowledgements
Changes; - All fixes implemented from supervisor feedback

    \item \textbf{Definition of terms}\\
    Specific definitions relevant to the literature review are initially defined.

@@

\section{Definition of terms}
Throughout the paper, various terms are used to define elements of the authentication ceremony relevant to fingerprints verification. Explicit descriptions are, therefore, stated in this section. These are used to remove ambiguity and underlying associations readers may have for the words chosen.
\\\\
\textbf{\textit{Method of comparison}} - is the way a user assesses the encoding scheme. The most common example and the one used as default is ``Compare-and-Confirm'' (CaC). CaC, as the name suggests, is the \textit{comparison} of two fingerprints on different devices or mediums that are then \textit{confirmed}. The following sections explain alternative methods of comparisons.

\todo{Phase this section out - make sure to remove from the introduction layout of the section}

@@

\subsubsection*{Methods of comparison performance}
Aside 
from ``Compare-and-Confirm'' (CaC), there is ``Compare-and-Select'' (CaS) and ``Compare-and-Enter'' (CaE). CaS is the method where one device displays the fingerprint, and the other user is provided with several options. The user then has to choose the correct value from the list of candidates. If there is no match, the user must deny the connection attempt. The creation of CaS was due to concerns that CaC would be ``too easy'' for users leading to complacency and errors\cite{uzun2007usability}. The design of CaE is for scenarios where both devices might not have a display, i.e., pairing between a phone and a keyboard. One device displays the checksum. This checksum is then entered into the other device. The first device then compares the entered string and checks for a match.

>>>>

@@

@@

\subsubsection*{Methods of comparison performance}

Method of comparison is the way a user assesses the encoding scheme. The most common example and the one used as default is ``Compare-and-Confirm'' (CaC). CaC, as the name suggests, is the \textit{comparison} of two fingerprints on different devices or mediums that are then \textit{confirmed}.

Aside from ``Compare-and-Confirm'' (CaC), there is ``Compare-and-Select'' (CaS) and ``Compare-and-Enter'' (CaE). CaS is the method where one device displays the fingerprint, and the other user is provided with several options. The user then has to choose the correct value from the list of candidates. If there is no match, the user must deny the connection attempt. The creation of CaS was due to concerns that CaC would be ``too easy'' for users leading to complacency and errors\cite{uzun2007usability}. The design of CaE is for scenarios where both devices might not have a display, i.e., pairing between a phone and a keyboard. One device displays the checksum. This checksum is then entered into the other device. The first device then compares the entered string and checks for a match.
